---
bibliography: references.bib 
authors: # see https://quarto.org/docs/journals/authors.html for further options
  - name: Firstname Lastname
    orcid: 0000-0001-0002-0003
    affiliation: "Your University"
    country: CountryABC
---

# PC Algorithm for Causal Discovery

| Resource | Information |
|----|----|
| Data DOI | [10.5281/zenodo.1234567](10.5281/zenodo.1234567) |
| Git + DOI | [Git](https://github.com/username/project) [10.5281/zenodo.7654321](10.5281/zenodo.754321) |
| Short Description | Short description of the main contributions and notebook structure |

: {.striped}

## Introduction

Write an introduction to the analysis. Give references via @Mareis_Haug_Drton_2025.

## Loading the Data

Create an R environment and save it in the file `renv.lock` with `renv::snapshot()`. 
Load the R environment with our standardized loading function.
```{r, message=TRUE, warning=TRUE, eval=TRUE}
source("../../load_environment.R")
```

Shortly describe the packages that were responsible for the R environment.
```{r, message=FALSE, eval=FALSE}
# Used packages, only for information.
library(package1) # function of package1
library(package2) # function of package2
```

Load the data. Prefereably from Zenodo:
```{r, message = FALSE, warning=FALSE}
# Load Data
zenodo <- ZenodoManager$new(logger = NULL)
record <- zenodo$getRecordByDOI("10.5281/zenodo.1234567")
files <- record$listFiles(pretty = TRUE)
alarm <- as.matrix(read.csv(files[1, 4]))
```

## Analysis 


```{r, message=FALSE, warning=FALSE, eval=TRUE}
source("../../close_environment.R")
```

## Citing this Notebook {.unnumbered}

Please cite XYZ with the following bib item.

``` bibtex
@article{XYZ
}
```

When using the ABC dataset, please give credit to the original author: Author

## Additional Information {.unnumbered}

**License Information:** Please follow the above DOI for license information of data and code.

**Contact:** If you have suggestions, feel free to [create an issue](https://github.com/username/git-project/issues) or contact the authors (your@mail.address).
